---
title: "Michele Claibourn"
output:
  html_document:
    css: style.css
    toc: yes
    toc_depth: 2
    toc_float: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(magrittr)
library(glue)
library(googlesheets4)
library(metathis)

# Public website, public sheet
googlesheets4::gs4_deauth()
projects_data <- read_sheet("https://docs.google.com/spreadsheets/d/1DfStXhr78NvVlSF0oBs5XrwSeoZWMqjRI9EEVYHwHh4/edit?usp=sharing")

htmltools::tagList(rmarkdown::html_dependency_font_awesome())

meta() %>%
  meta_description(
    "A portfolio of my political science, data science, and community-engaged research projects"
  ) %>%
  meta_name("github-repo" = "mclaibourn/mclaibourn.githubub.io") %>% 
  meta_name("google-site-verification" = "Bl7V9ToZ3Hfn6misjeF-7zKcK2qrpBY76p26xAE0dIg")
```

I am a research director – social scientist, data scientist, community-engaged scholar, and administrator – and faculty member with 20+ years of experience teaching, leading, and managing research and data science teams. 

I work as the Director of Equitable Analysis in [The Equity Center](https://virginiaequitycenter.org) at the University of Virginia working with an amazing collection of scholars and practitioners, community experts, and students to create analysis and tools in support of a more just and equitable region. I also teach in the [Batten School of Leadership in Public Policy](https://batten.virginia.edu/), focusing on data ethics, public interest technology, and equitable policy, and am an affiliated faculty with the [School of Data Science](https://datascience.virginia.edu).

I have been fortunate to engage in a wide variety of work -- as a political science professor and quantitative scholar at the University of Oklahoma and the University of Virginia; as a data scientist engaged in applied work with the [Weldon Cooper Center for Public Service](https://demographics.coopercenter.org/); as a consultant and leader creating [UVA's StatLab](https://data.library.virginia.edu/statlab/); as a library director building [Research Data Services and the Social, Natural, and Engineering Sciences](https://data.library.virginia.edu/); and as a researcher bridging applied and academic interests with community partners and advocates. 

And I've been grateful to find many generous and creative partners along the way who've invited me to be part of collaborative work, including:

* Community Policy, Analytics, and Strategy Lab ([CommPAS](https://commpas.batten.virginia.edu/)), co-directing a community-oriented research initiative with [Paul Martin](https://batten.virginia.edu/people/paul-martin) in the Batten School of Public Policy,
* [UVA Legal Data Lab](https://legaldatalab.law.virginia.edu/), working to develop a platform to make anonymized court record data from the Virginia Judiciary more accessible for use by researchers and advocates,
* The Global Policy Center's [Humanitarian Collaborative](https://humanitariancollaborative.com/) at UVA, working on predictive analytics for humanitarian goals,
* [The RVA Eviction Lab](https://rampages.us/rvaevictionlab/) at VCU, building data tools to support activists and advocates fighting harmful evictions.
* [The Environmental Institute](https://environment.virginia.edu/) at UVA, working with an interdisciplinary team to translate science into data-rich decision support tools for the Eastern Shore of Virginia.

My own work centers on action-based research, using the tools of data science to promote accountable governance, make visible racial and other social inequities, and impact public policy and movement building. More importantly, I hope I'm mentoring the incredible young people I get to work with at UVA to engage this work early in their careers.

Also, sometimes I play the mandolin, pretend I'm learning to play the banjo, and harbor a dream of joining a [home-grown bluegrass band](https://www.facebook.com/StPaulsMemorialChurch/videos/1351361454880067/)! 

## CV/Resume

See a mostly complete CV | And a brief resume 
-------- | --------
* [html version](mpc_cv.html) | * [html version](mpc_resume.html)
* [pdf version](pdf/mpc_cv.pdf) | * [pdf version](pdf/mpc_resume.pdf)


## Community-Engaged Projects

Some examples of recent community-oriented projects, done as part of the current Equity Center work and previous community work through the CommPAS Lab. 

```{r, results = 'asis'}
projects_gathered <- projects_data %>% 
  filter(category == "community") %>% 
  mutate(id = 1:n()) %>% 
  mutate_all(~ifelse(. == "NA", NA, .)) %>% 
  pivot_longer(
     starts_with('description'),
     names_to = 'description_num',
     values_to = 'description',
     values_drop_na = TRUE
   ) %>% 
  group_by(id) %>% 
  mutate(description_bullets = paste0("<li>", description, "</li>", collapse = "\n") ) %>% 
  ungroup() %>% 
  filter(description_num == 'description_1') 
github_icon <- "<i class='fa fa-github fa-lg' style='padding-right:5px' aria-hidden='true'></i>"
link_icon <- "<i class='fa fa-home fa-lg' style='padding-left:5px' aria-hidden='true'></i>"
projects_gathered %>% 
  mutate(
    github_link = ifelse(
      is.na(github), 
      "", 
      glue("<a href='{github}'>{github_icon}</a>")
    ),
    main_link = glue("<a href='{link}'>{link_icon}</a>"),
    all_links = glue("<p class='links'>{github_link} {main_link}</p>")
  ) %>% 
  glue_data(
    "<div class='project-entry'>",
      "<h3> <a href='{link}'>{title}</a> </h3>",
      "<div class='photo_and_description'>",
        "<img src='{photo}'>",
        "<div class='description'>",
          "<ul class='description-list'> {description_bullets} </ul>",
          "{all_links}",
        "</div>",
      "</div>",
    "</div>", 
    "<hr>"
  )
```


## Teaching and Instruction

Current courses and past workshops, instructional blog posts, and other projects and materials created as educational resources.

```{r, results = 'asis'}
projects_gathered <- projects_data %>% 
  filter(category == "instruction") %>% 
  mutate(id = 1:n()) %>% 
  mutate_all(~ifelse(. == "NA", NA, .)) %>% 
  pivot_longer(
     starts_with('description'),
     names_to = 'description_num',
     values_to = 'description',
     values_drop_na = TRUE
   ) %>% 
  group_by(id) %>% 
  mutate(description_bullets = paste0("<li>", description, "</li>", collapse = "\n") ) %>% 
  ungroup() %>% 
  filter(description_num == 'description_1') 
github_icon <- "<i class='fa fa-github fa-lg' style='padding-right:5px' aria-hidden='true'></i>"
link_icon <- "<i class='fa fa-home fa-lg' style='padding-left:5px' aria-hidden='true'></i>"
projects_gathered %>% 
  mutate(
    github_link = ifelse(
      is.na(github), 
      "", 
      glue("<a href='{github}'>{github_icon}</a>")
    ),
    main_link = glue("<a href='{link}'>{link_icon}</a>"),
    all_links = glue("<p class='links'>{github_link} {main_link}</p>")
  ) %>% 
  glue_data(
    "<div class='project-entry'>",
      "<h3> <a href='{link}'>{title}</a> </h3>",
      "<div class='photo_and_description'>",
        "<img src='{photo}' height='200'>",
        "<div class='description'>",
          "<ul class='description-list'> {description_bullets} </ul>",
          "{all_links}",
        "</div>",
      "</div>",
    "</div>", 
    "<hr>"
  )
```


## Research Projects

More academically-oriented work

```{r, results = 'asis'}
projects_gathered <- projects_data %>% 
  filter(category == "research") %>% 
  mutate(id = 1:n()) %>% 
  mutate_all(~ifelse(. == "NA", NA, .)) %>% 
  pivot_longer(
     starts_with('description'),
     names_to = 'description_num',
     values_to = 'description',
     values_drop_na = TRUE
   ) %>% 
  group_by(id) %>% 
  mutate(description_bullets = paste0("<li>", description, "</li>", collapse = "\n") ) %>% 
  ungroup() %>% 
  filter(description_num == 'description_1') 
github_icon <- "<i class='fa fa-github fa-lg' style='padding-right:5px' aria-hidden='true'></i>"
link_icon <- "<i class='fa fa-home fa-lg' style='padding-left:5px' aria-hidden='true'></i>"
projects_gathered %>% 
  mutate(
    github_link = ifelse(
      is.na(github), 
      "", 
      glue("<a href='{github}'>{github_icon}</a>")
    ),
    main_link = glue("<a href='{link}'>{link_icon}</a>"),
    all_links = glue("<p class='links'>{github_link} {main_link}</p>")
  ) %>% 
  glue_data(
    "<div class='project-entry'>",
      "<h3> <a href='{link}'>{title}</a> </h3>",
      "<div class='photo_and_description'>",
        "<img src='{photo}'>",
        "<div class='description'>",
          "<ul class='description-list'> {description_bullets} </ul>",
          "{all_links}",
        "</div>",
      "</div>",
    "</div>", 
    "<hr>"
  )
```

## Library Projects

Projects done on behalf of library units and initiatives.

```{r, results = 'asis'}
projects_gathered <- projects_data %>% 
  filter(category == "library") %>% 
  mutate(id = 1:n()) %>% 
  mutate_all(~ifelse(. == "NA", NA, .)) %>% 
  pivot_longer(
     starts_with('description'),
     names_to = 'description_num',
     values_to = 'description',
     values_drop_na = TRUE
   ) %>% 
  group_by(id) %>% 
  mutate(description_bullets = paste0("<li>", description, "</li>", collapse = "\n") ) %>% 
  ungroup() %>% 
  filter(description_num == 'description_1') 
github_icon <- "<i class='fa fa-github fa-lg' style='padding-right:5px' aria-hidden='true'></i>"
link_icon <- "<i class='fa fa-home fa-lg' style='padding-left:5px' aria-hidden='true'></i>"
projects_gathered %>% 
  mutate(
    github_link = ifelse(
      is.na(github), 
      "", 
      glue("<a href='{github}'>{github_icon}</a>")
    ),
    main_link = glue("<a href='{link}'>{link_icon}</a>"),
    all_links = glue("<p class='links'>{github_link} {main_link}</p>")
  ) %>% 
  glue_data(
    "<div class='project-entry'>",
      "<h3> <a href='{link}'>{title}</a> </h3>",
      "<div class='photo_and_description'>",
        "<img src='{photo}'>",
        "<div class='description'>",
          "<ul class='description-list'> {description_bullets} </ul>",
          "{all_links}",
        "</div>",
      "</div>",
    "</div>", 
    "<hr>"
  )
```

